DRAFT Example Kitsap County Pedestrian Facilities Metrics/Evaluation Report

### 2022-10-03 Draft Ped Metrics Example.Rmd
replace df risk with loop_df to avoid overwrite with temporary df

```{r loop_lamirds,include=FALSE,echo=FALSE}
the_lamirds <- unique(st_set_geometry(lamird, NULL)$PLAN_AREA)
df <- st_as_sf(lamird) %>% mutate(tomatch = PLAN_AREA)

>>>>

```{r loop_lamirds,include=FALSE,echo=FALSE}
the_lamirds <- unique(st_set_geometry(lamird, NULL)$PLAN_AREA)
loop_df <- st_as_sf(lamird) %>% mutate(tomatch = PLAN_AREA)

### 2022-10-03 child_single_geo.Rmd
replace df risk with loop_df to avoid overwrite with temporary df

```{r} 
library(broom)
this_geo <- st_as_sf(df) %>% filter(tomatch == "{{current_geo}}") 
this_roads <- st_intersection(road_df, st_buffer(this_geo,0))
this_sw_sh <- st_intersection(nc_sw_sh, st_buffer(this_geo,0))

>>>>

```{r} 
library(broom)
this_geo <- st_as_sf(loop_df) %>% filter(tomatch == "{{current_geo}}") 
this_roads <- st_intersection(road_df, st_buffer(this_geo,0))
this_sw_sh <- st_intersection(nc_sw_sh, st_buffer(this_geo,0))
